\documentclass[11pt,a4paper]{article}
\input{format}

\setlength {\textwidth}{165mm} 
\setlength {\textheight}{255mm}
\topmargin=-15.00mm
\oddsidemargin=-5.0mm

\begin{document}

   \title{Supplemental Material for J110057}
\maketitle


\section*{Further Observational Details}

\subsection*{Selection in SDSS-III BOSS of J110057}
SDSS J110057.71-005304.5 was first detected by the ROSAT
and appears in the All-Sky Survey Bright Source Catalogue
\citep[RASS-BSC; ][]{Appenzeller1998, Voges1999}. 
J110057 was then imaged by the Sloan Digital Sky
Survey and satisfied a number
of spectroscopic targeting flags\footnote{SERENDIP\_BLUE, ROSAT\_D,
ROSAT\_C, ROSAT\_B, QSO\_SKIRT, ROSAT\_A, see \citet{EDR} and
\citet{Richards2002} for flag descriptions.}  making it an SDSS quasar
target. A spectrum was obtain on MJD 51908 (Plate 277, Fiber 212)
and the spectrum of a $z=0.378$ quasar was catalogued in the
SDSS Early Data Release \citep{Schneider2002}. The physical properties
of J110057, derived from the MJD 51908 spectrum and using the methods
in \citet{Shen2011}, are given in Table~\ref{tab:Shen_props}.

\begin{table}[]
    \centering
    \begin{tabular}{l l }
      \hline \hline 
      Quantity                                         &  Value \\
      \hline 
      SDSS name                                     &   J110057.71-005304.5 \\
      R.A. / deg                &  165.240463 \\
      Declination / deg    &   -0.884586 \\ 
      redshift, $z$                                    &   0.3778$\pm$0.0003  \\
      $M_{i}(z=2)$  / mag                          &   -24.48  \\
      log $(L_{\rm bol} / {\rm erg s}^{-1}) $  &  45.78$\pm$0.02 \\
      log $(M_{\rm BH} / M_{\odot})  $           &  8.83$\pm$0.14 \\
      Eddington ratio                                &        0.070 \\
      \hline \hline 
    \end{tabular}
    \caption{Physical properties of J110057 using the methods from 
      \citet{Shen2011}.} 
    \label{tab:Shen_props}
\end{table}

The second epoch spectrum is from the SDSS-III Baryon Oscillation
Spectroscopic Survey \citep[BOSS; ][]{Dawson2013} and shows the dramatic
downturn at $\lesssim$4300\AA\ .  SDSS-III BOSS actively vetoed {\it
against} low-$z$ QSOs \citep{Ross2012}, and it was due to J110057 being
selected as an ancillary target via a White Dwarf program
\citep{Kepler2015, Kepler2016} that a second spectral epoch was serendipitously
obtained.  Since J110057 was not a BOSS QSO target, it is not subject
to the ``blue offset'' present for BOSS QSO targets \citep{Margala2016}.

A third epoch spectrum was obtained from the Palomar 5m telescope
using the DBSP instrument.  Two exposures of 600s+300s were taken in
good conditions. Features to note include the continuum straddling
\mgii being blue in the 2017 spectrum, as it was for the SDSS spectrum
in 2000, as opposed to red, as it was for the BOSS spectrum in 2010.

J110057 is in the DECaLS DR3, where there are 8, 3 and 9 exposures in
the $g$, $r$ and $z$-band respectively. The $g$- and $r$-band
observations have fairly limited time spans, ($56707 \leq g_{\rm MJD}
\leq 56727$ and $56367 \leq r_{\rm MJD} \leq 56367$) and are separated
by roughly a year. The $z$-band observations span almost 3 years
($56383 \leq z_{\rm MJD} \leq 57398)$.  The DESI imaging brick name is
1651m010.


\subsection*{Selection in NEOWISE-R of J110057}
%%  This is text from Aaron's email from 15th Feb, 2017, sent to Daniel, 
%%  for the WISE J1052+1519 outline/paper

WISE W1 and W2 lightcurves for $\sim$200,000 SDSS spectroscopic
quasars were extracted from Data Release 3 (DR3) of the Dark Energy
Camera Legacy Survey (DECaLS). These light curves span from the
beginning of the WISE mission (2010 January) through the first-year of
NEOWISER operations (2014 December). The W1/W2 light curves are
obtained by performing forced photometry at the locations of
DECam-detected optical sources \citep{Lang2014, Meisner2017a,
Meisner2017b}.  This forced photometry is performed on time-resolved
unWISE coadds \citep{Lang2014}, each of which represents a stack with
depth of coverage $\sim$12 exposures. A given sky location is observed
by WISE for $\sim$1 day once every six months, which means that the
forced photometry light curves typically have four coadd epochs
available. Coadd epochs of a given object are separated by a minimum
of six months and a maximum of four years. The coaddition removes the
possibility of probing variability on $\lesssim$1 day time scales, but
it allows us to push $\approx$1.4 magnitudes deeper than individual
exposures while removing virtually all single-exposure artifacts
(e.g. cosmic rays and satellites).

Approximately $\sim$30,000 {\bf NPR NOTE:: This number seems low to
me; NPR to double check; can also triple check with Aaron} of the
SDSS/BOSS quasars with such W1/W2 light-curves available are
``IR-bright'', in the sense that they are above both the W1 and W2
single exposure thresholds and therefore detected at very high
significance in our coadds. For this ensemble of objects, the typical
variation in each quasar's measured (W1-W2) color is 0.06 magnitudes,
which includes statistical and systematic errors expected to
contribute variations at the few hundredths of a mag level. The
typical measured single-band scatter is 0.07 magnitudes in each of W1
and W2.

We undertook a search for extreme outliers relative to these trends.
Specifically, we selected objects with the following characteristics:
\begin{itemize}
    \item Monotonic variation in both W1 and W2.
    \item W1 versus W2 flux correlation coefficient $>$0.9.
    \item $>0.5$ mag peak-to-peak variation in either W1 or W2.
\end{itemize}
This yielded a sample of 248 sources. 31 of these are assumed to be
blazars due to the presence of FIRST radio counterparts. Another 22
are outside of the FIRST footprint, leaving 195 quasars in our
IR-variable sample.

A link to the key properties of our sample can be found here:
\href{http://portal.nersc.gov/project/cosmo/temp/ameisner/qso\_pages\_v01/}
{\tt qso\_pages\_v01} and the links to the catalogs are given here:
\href{http://portal.nersc.gov/project/cosmo/temp/ameisner/dr3_wise_lc_sample.fits.gz}{{\tt
dr3\_wise\_lc\_sample.fits.gz}} and here:
\href{http://portal.nersc.gov/project/cosmo/temp/ameisner/dr3_wise_lc_metrics_all_qso.fits.gz}{{\tt
dr3\_wise\_lc\_sample.fits.gz}}.  The first catalog has 248 rows,
which are the selected highly IR-variable sample of objects.  The
second catalog is the full \hbox{200 622} quasar sample quasars that
have ``good'' WISE light curves available in DECaLS DR3. In each file,
there are 3 extensions: the first extention are the WISE light curve
summary metrics; the second extension the DECaLS DR3 data for each
object, and the third extenion, the SDSS data for each object.
A full characterization of the typical mid-IR quasar variability will be
presented separately.

\subsection*{Additional Multiwavelength data}
Checking the data archives we found there was no source within 30
arcsec in the VLA FIRST, i.e., at 21 cm radio frequencies.  None of
the {\it Hubble Space Telescope}, the {\it Spitzer Space Telescope} or
the {\it Kepler} Mission has observed J110057.  It is also not in the
HSC DR1 footprint.  There is the detection in ROSAT (which tirggers  using the 2nd
all-sky survey (2RXS; Boller et al. 2016, A\&A, 588, 103) as 2RXS
J110058.1-005259 with 27.00 counts (count error 6.14) and a count rate
= 0.06$\pm$0.01. The NED gives J110057 as $1.27\pm0.28 \times^{-12}$
erg/cm$^{2}$/s in the 0.1-2.4 keV range (unabsorbed flux). J110057 is
not in either {\it Chandra} or {\it XMM-Newton}.



\section*{Further Model Details}
%— Nic, Saavik, Barry to begin to sketch-up a “cartoon” to show the
%time evolution of the a model and system here. This sound look to
%include descriptions of the the e.g. sound speed, disk height and
%pressure support as the cooling front propagates out and the heating
%front gets established and propagates inward.

Our model consists of three main stages: {\it (i)} an event that causes
an initial change of torques at the ISCO; {\it (ii)} the propagation
of an cooling front in the accretion disk, outward from the central
engine with an associated increase in the number density of scatterers
and {\it (iii)} a propagation back in towards the central black hole of a
heating front, leading to a `recovery' in the observed spectra.

The current dataset and observations of J11057 means we remain agnostic to
the event(s) that causes the initial change of torques at the
ISCO.  A change in magnetic field being the cause of non-zero torques
is well studied, see e.g., \citet{Krolik1999, Gammie1999,
Agol_Krolik2000, Reynolds_Armitage2001}, but we currently 
cannot confirm this. Notably,
\citet{Afshordi_Paczynski2003} argue that a thick disk at the ISCO
should produce a substantial torque, while a thin one will not.
Regardless of the initial trigger, we suggest some event causes 
a change in the torque conditions at the ISCO. As such, we build 
on the non-zero torque model from \citet{Zimmerman2005}. 

For the second stage of our model, we need to explain the
observed light-curves and optical spectra. J110057 changes from
$\approx$17.9mag to $\approx$18.5mag in the observed $g$-band over
$\lesssim$100 days (in the observed frame).  This translates to a
Johnson V-band flux density change from 0.262 mJy to 0.151 mJy.
However, given the redshift of $z=0.378$, the observed V-band
380-750nm corresponds to 276-544nm in the rest frame ($-6.56 < \log
\lambda < -6.26$) or near-UV to red in the quasar frame. The source
flux density drops to 58\% of the original flux in $\sim$3 months.

Simply changing the boundary condition at $R_{\rm in}$ from non-zero
torque to zero torque (e.g. collapsing a puffed-up disk inner edge,
or, as mentioned above, the magnetic fields) leads to the difference
in the SEDs ({\bf NPR NOTE:: Figures 6 and 7 in the notes}).  At $\log
\lambda = −6.56$, the flux for $R_{in} = 9 r_{g}$ %(dark blue in both)
drops by $\sim0.2$ dex from $\sim38.0$ to $\sim37.8 $ or from $10.0$
to 6$\times 10^{37}$ ergs), or to 60\% of the initial flux density,
consistent with the values above.

In the restframe spectrum, however, the 300 nm flux seems to drop by a
factor of $\sim$5 (given the uncertainty in the normalization). The
flux at $\lambda < 350$ nm is dropping relative to the optical
flux. In order to make the multi-color blackbody spectrum do this, 
large regions of the  inner disk have to dim simultaneously. 
For example, if the entire inner disk at $R \leq 50 r_{g}$ changed state
and became dimmer on thermal timescales at each annulus, we can
reproduce both the change at short wavelengths and the observed V-band
change.

\citet{Gardner_Done2017} present observational evidence (see their
figure 7 cartoon) for an interior puffy structure while
\citet{Jiang_Stone_Davis2016} examine in detail the effects of the
bound-bound transitions in iron and the his iron opacity ``bump'', on
the thermal stability and vertical structure of
radiation-pressure-dominated accretion disks, relevant in UV emitting
regions of the accretion disk flow.



\subsection*{Relevant Timescales}
There are several relevant timescales associated with J110057 and our
model explaining the observations. These are given in
Table~\ref{tab:timescales}, where we parameterize the relevant disk
timescales at $R\sim 50 r_{g}$ as:
%``Relevant disk timescales around a $M_{\rm BH} = 10^{8} M_{\odot}$ at $R\sim 25r_{g}$ are:''
\begin{table}
  \centering
  \begin{tabular}{ l c c }
\hline \hline
    Description           &                             & quantity \\
\hline  
&& \\
Orbital                      & $t_{\rm orb}$          &  $6\; {\rm days}
                                                                     \left( \frac{R}{50 r_{g}}  \right)^{3/2}
                                                                    \left( \frac{ r_{g}}{c} \right)$\\
&& \\
Thermal                    &  $t_{\rm thermal}$    &  $6 \; {\rm months} 
                                                                        \left( \frac{\alpha}{0.03}  \right)^{-1}
                                                                        \left( \frac{R}{50 r_{g}}  \right)^{3/2}
                                                                       \left(  \frac{ r_{g}}{c}\right)  $ \\
&& \\
Front propagation   & $t_{\rm front}$             & $11 {\rm yr}
                                                                         \left( \frac{h/R}{0.05}  \right)^{-1}
                                                                         \left( \frac{\alpha}{0.03}  \right)^{-1}
                                                                        \left( \frac{R}{50 r_{g}}  \right)^{3/2}
                                                                     \left( \frac{ r_{g}}{c}\right)$\\
&& \\
 Cloud-crushing      &  $t_{\rm cc}$             &   $100\; {\rm yr} \; 
                                                                       \left(  \frac{  \rho_{\rm cloud}/\rho_{\rm medium}}{10^6}  \right )^{1/2} 
                                                                       \left( \frac{R}{4\times10^{10} \rm{km}} \right)
                                                                     \left(\frac{V_{\rm rel}}{10^4 {\rm \; km/s }} \right)^{-1} $\\
&& \\
viscous                     & $t_{\rm \nu}$             & $230 {\rm yr}
                                                                         \left( \frac{h/R}{0.05}  \right)^{-2}
                                                                         \left( \frac{\alpha}{0.03}  \right)^{-1}
                                                                        \left( \frac{R}{50 r_{g}}  \right)^{3/2}
                                                                      \left( \frac{ r_{g}}{c} \right)$\\
&& \\
\hline \hline
    \end{tabular}
    \caption{Here, $\alpha$ is the viscosity of the disk; $\rho_{\rm cloud}$ is ; $\rho_{\rm medium}$ is  ;
      $R$ is the radius of the accretion disk; $r_{g}$ is the Gravitational radius; 
      $V_{\rm rel}$ is .}
    \label{tab:timescales}
    \centering
  \end{table}


\section*{Comparison with SDSS J2317+0005 from Guo et al. 2016}
Figure~1 of Guo et al. (2016) shows a UV collapse in the 
quasar SDSS  J231742.60 +000535.1 (hereafter J2317+0005, 
$z=0.32$) at a very similar wavelength to that in the 2010
spectrum of J110057, and with turnovers in both around
$\sim$350 nm.  The collapse in J2317+0005 happens in 23 days \citep[Figure 2
of ][]{Guo2016} and this object was observed with SDSS back on MJD
52177 (normal) and then 23 days later on MJD 52200. There is a drop of
1.2mag in the $u$-band and 0.5mag in $g$-band, with $r,i,z$ are all
consistent with the earlier observation. J23 is observed with SDSS
again about a year later and $(u,g,r,i,z)$ are all back consistent
with `normal'. More importantly, XMM-Newton spectra straddle this time
period. The XMM-Newton spectra are from June 3 and Nov. 28 2001. Both
spectra are consistent with {\it no neutral absorption in the
rest-frame}. So the sightline is clear on both of those dates
(i.e. the Nov. spectrum is 45 days after the UV
catastrophe). \citet{Guo2016} also find that the IR does not
significantly change and that the broad lines are consistent with
being constant over time.

\citet{Guo2016} discuss two scenarios to explain this behaviour: 1)
inner accretion disk change and 2) eclipse by an optically thick
cloud. They make the point that in principle both models could explain
the observation. In scenario 1) they suggest that turning off the disk
at $< 60 r_{\rm g} = 30 r_{\rm Sch}$ would explain this (in the same
manner as we discuss for J11057) but they find this implausible since
``quasars are not observed to flicker like this typically''.
\citet{Guo2016} then spend more time on scenario 2). So, based on the
initial optical spectrum (23 days before the $u$-band dip) and the
Nov. X-ray spectrum (45 days after the $u$-band dip) they say that the
dip lasts $< 65$ days.



\bibliographystyle{mn2e}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}


\end{document}